Open source symbolic multibody dynamics software

### 2012-03-05 PetersonGedeHubbard2012.tex
Added abstract and changed some keywords.

\begin{abstract}
  Abstract here.
\keywords{symbolic dynamics software, control, nonholonomic systems,
          constrained systems}
\end{abstract}

@@

There are a number of additional steps needed to use these linear equations or
form them more efficiently. There are also non-singularity requirements
involved in selection of independent quantities.

@@

If it is found that substatial computational time is spent in computing the
jacobian matrices, it might be possible to reduce the time if the point of
linearization is known. We are taking the partial derivatives with respect to
$q$, $\dot{q}$, $u$, and $\dot{u}$ in a number of vectors. If we know the point
of linearization (have numerical values for $q$, $\dot{q}$, $u$, $\dot{u}$), we
can substitute all of the quantities except for those we are taking the
derivative with respect to; e.g. when computing $\nabla_{\mb{u}} \bm{f}_3$ we
substitute in the known values for $q$, $\dot{q}$, and $u$. In this situation,
the cost of symbolic substitution needs to be considered. In practice, it has
sometimes been computationally expensive. The potential speed-up needs to be
considered next to the loss of generality of choosing a point of linearization
after the fact.

>>>>

\begin{abstract}
  We present a systematic procedure for linearizing equations of motion
  governing constrained multibody systems which have been derived with Kane's
  method.  Systems with configuration and velocity level constraints are
  address by the procedure.  The procedure avoids differential algebraic
  equations and yields first order relationships between time derivatives of
  generalized coordinates/speeds (both independent and dependent) and
  independent generalized coordinates/speeds and exogenous inputs.  The
  procedure enables stability analysis and control system design in a fashion
  that ensures that all constraints are satisfied.  We present an
  implementation of the algorithm and numerically validate the results on a
  well studied model of a bicycle.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

@@

There are a number of additional steps needed to use these linear equations or
lorm them more efficiently. There are also non-singularity requirements
involved in selection of independent quantities.

@@

If it is found that substatial computational time is spent in computing the
jacobian matrices, it might be possible to reduce the time if the point of
linearization is known. We are taking the partial derivatives with respect to
$q$, $\dot{q}$, $u$, and $\dot{u}$ in a number of vectors. If we know the point
of linearization (have numerical values for $q$, $\dot{q}$, $u$, $\dot{u}$), we
can substitute all of the quantities except for those we are taking the
derivative with respect to; e.g. when computing $\nabla_{\bm{u}} \bm{f}_3$ we
substitute in the known values for $q$, $\dot{q}$, and $u$. In this situation,
the cost of symbolic substitution needs to be considered. In practice, it has
sometimes been computationally expensive. The potential speed-up needs to be
considered next to the loss of generality of choosing a point of linearization
after the fact.
